A hierarchical approach for modelling X-ray beamlines. Application to a coherent beamline.

### 2019-03-24 paper-hierarchical.tex
changed order in bib files
starting text

\begin{abstract}
This paper shows different approaches to simulate a modern X-ray beamline. It considers different methodologies with 
increasing complexity as it goes from simple hand-calculations to the most sophisticated available computer simulations based on both ray tracing and waveoptics techniques. A last generation nanofocusing beamline for coherent x-ray applications has been chosen (ID16A at the ESRF) to study in detail the issues 
related to highly demagnifying sychroton sources and exploiting the beam coherence. The performance of the beamline is studied for two storages rings: the old ESRF (emittance 4000 pm) and the new ESRF-EBS (emittance 150 pm). This document gives results in term of flux, intensity distribution, focal size, and partial coherence properties using different software tools. The different algorithms and methodologies are discussed with emphasis in benefits and limitations of each one. 
\end{abstract}

@@

\todo{To be written... 1) Introduction to nanofocus and coherent applications 2) ID16a 3) methods and contents 4) OASYS}

@@

\bibliography{paper-hierarchical}
\bibliographystyle{iucr}

>>>>

\begin{abstract}
We consider different approaches to simulate a modern X-ray beamline. Several methodologies with increasing complexity are applied to discuss the relevant parameters that quantify the beamline performances. Parameters such as flux, beam size at the image and coherence properties are obtained from simple hand-calculations to sophisticated computer simulations using ray tracing and waveoptics techniques. A last generation x-ray nanofocusing beamline for coherent  applications (ID16A at the ESRF) has been chosen  to study in detail the issues 
related to highly demagnifying sychrotron sources and exploiting the beam coherence. The performance of the beamline is studied for two storages rings: the old ESRF (emittance 4000 pm) and the new ESRF-EBS (emittance 150 pm). This document gives results in term of flux, intensity distribution, focal size, and partial coherence properties using different software tools. The different algorithms and methodologies are discussed with emphasis in benefits and limitations of each one. 
\end{abstract}

@@

1) Introduction to nanofocus and coherent applications

2) ID16a

3) methods and contents

4) OASYS

@@

\bibliographystyle{iucr}
\bibliography{paper-hierarchical}
